### 2023-03-13 resilience.tex
Up
up

@@

>>>>

% $Bad$ still necessarily contains $0$, and $0 \rightarrow^* 0$.

$Bad = J_1 \cup J_2 \cup \ldots \cup J_m$

$Safe = I_1 \cup I_2 \cup \ldots \cup I_n$

Question is: can we reach one of the $I_i$ from one of the $J_j$ ?

If the ideal reachability problem is decidable then of course the question here should be decidable as well.

But it may be possible to do more i.e.

If we can express $\downarrow Post( J_j)$ then the question become:
is $Safe \cap \cup_{j} \downarrow Post( J_j) \neq \emptyset$ ?

(we need to reach an element of $Safe$ but not every possible element)

@@

If $Safe = \downarrow 0$ and $Bad = \uparrow s$ . . .

Then resilience kinds of becomes "can we reach $0$ from $\uparrow s$?".

In a reset petri-net, if $Bad = \uparrow q_0(\mu)$ for some $\mu \neq 0$,
and $Safe = \downarrow q(0)$,
then the resilience problem is basically \textcolor{red}{(is it?)} the single-state zero-reachability problem, and is undecidable.

\mathieu{Ici}
